Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-15 icse/paper.tex
Relation

\subsubsection{Clone Token Volume}
Figure \ref{fig:duplication} shows the obtained results when plotting the clone size (in tokens) vs the maintainability increase/decrease. On the secondary axis the amount of refactorings that have refactored a clone with the specified amount of tokens is displayed (e.g. the amount of datapoints the data is based on). As the amount of datapoints decreases, the datapoints become more noisy.

@@

>>>>

\subsubsection{Clone Token Volume}
Figure \ref{fig:duplication} shows the obtained results when plotting the clone size (in tokens) vs the maintainability increase/decrease. On the secondary axis the amount of refactorings that have refactored a clone with the specified amount of tokens is displayed (e.g. the amount of datapoints the data is based on). As the amount of datapoints decreases, the datapoints gain less statistical significance.

@@

\subsubsection{Relation}
Table \ref{} shows our data regarding how different relations influence maintainability. We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance. For these results, we have set the minimum amount of tokens for clones to 18 because otherwise the small clones dominate the results and turn them all towards unmaintainable.

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Row Labels & Maintainability Score & Number of Refactorings \\ \midrule
\rowcolor[HTML]{FFCCC9}
Common Hierarchy & 0,63 & 27 \\
Sibling & 0,53 & 664 \\
No Direct Superclass & 0,11 & 295 \\
Same Method & 0,06 & 740 \\
\rowcolor[HTML]{FFCCC9}
Superclass & 0,03 & 68 \\
Same Class & 0,02 & 1273 \\
External Superclass & 0,01 & 209 \\
\rowcolor[HTML]{FFCCC9}
No Indirect Superclass & -0,06 & 36 \\
Same Interface & -0,07 & 269 \\
\rowcolor[HTML]{FFCCC9}
First Cousin & -0,19 & 54 \\
External Ancestor & -0,28 & 154 \\
\rowcolor[HTML]{FFCCC9}
Ancestor & -0,52 & 5 \\ \bottomrule
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}
